---
title: "STEGO"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STEGO}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Single cell TCR and Expression Grouped Ontologies (STEGO) was built for standardising the processing and analysis of single cell (sc) RNA-seq with T cell receptor (TCR) seq datasets. 

Please refer to the online tutorial https://stegor.readthedocs.io/en/latest/ for more details. Follow the installation of R with the corresponding dependencies depending on the system. 

Pre-installation dependencies.

```{r, echo=TRUE}
# see https://stegor-documents.readthedocs.io/en/latest/index.html for more details on the tutorial to follow through.
# This is to make sure with installing from source is set to the g++ compiler
Sys.setenv("CXX" = "g++")

# installing STEGO.R
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

if (!require("devtools", quietly = TRUE))
  install.packages("devtools")

if (!require("usethis", quietly = TRUE))
  install.packages("usethis")

```

install STEGO.R with Devtools

```{r, echo=TRUE}

if (!require("STEGO.R"))
  devtools::install_github("KerryAM-R/STEGO.R")

```

If asked to update the app either select 1 to updated all
1

If asked to install from source on the M1 Mac chip (Seurat)
y

If then prompted with all the bioconductor based packages to install from source on M1 or greater Mac chip
y


import all of the fonts to your system. Will only need to be done the first time.

```{r, echo=TRUE}
if (!requireNamespace("extrafont", quietly = TRUE)) {
  install.packages("extrafont")
}
extrafont::font_import()
```

If you haven't downloaded the formatted project directory from the tutorial https://stegor.readthedocs.io/en/latest/ you can also download it using this command. 

```{r, echo=TRUE}
if (!requireNamespace("utils", quietly = TRUE)) {
  install.packages("utils")
}

utils::download.file("https://raw.githubusercontent.com/KerryAM-R/STEGO.R/main/Directory_for_Project.zip",
              destfile = "Directory_for_Project.zip")

```


This command will open up the Shiny window in your default browser. 

```{r, echo=TRUE}
library(STEGO.R)

# STEGO.R::runSTEGO() 
```

There are several functions available in addition to the interface. These scripts are availabe in the folder_for_project. 

Step 1. pre-processing

Step 2b. ClusTCR2_large.R

Step 3a-c. filtering_merging_harmony_annotating.R

See the scripts for details. 
